---
title: "Lab 01 - Hello R"
author: "Lindley Slipetz"
date: "January 28th, 2021"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE, warning = FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

This dataset has 1846 rows and 3 columns. The variables are dataset, x-values, and y-values.

```{r freq}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```

### Exercise 2

Dino plot:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Dino correlation:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Star plot:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Star correlation:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
The correlations for dino data and star data are very close.

### Exercise 4

Circle plot:

```{r circle_plot}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Circle correlation:

```{r circle_corr}
circle_data %>%
  summarize(r = cor(x, y))
```
The correlation for circle is similar to the correlations for dino and star.
### Exercise 5

Add code and narrative as needed.
To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.
